Impacts of air pollution on investors' moods

### 2022-04-28 outputs/paper/paper.Rmd
finalized paper

>>>>

```{r}
# transform character variables to factors
masterdata$temp_bins <- as.factor(masterdata$temp_bins)
masterdata$dewp_bins <- as.factor(masterdata$dewp_bins)
masterdata$woy <- as.factor(masterdata$woy)
masterdata$dow <- as.factor(masterdata$dow)

# setup the equation
formula <- formula(log_ret ~ pm25 + lag1_ret + lag2_ret + PRCP + WDSP + SLP + VISIB + temp_bins + dewp_bins + SAD + dow + woy)

# setup needed list
garch_fits <- list()
lm_fits <- list()
return_models <- list()
n <- vector()
city <- vector()

# make the loop for building models for all cities
for (i in unique(AS$city)) {

  data <- AS[AS$city == i, ]
  data <- AS[AS$city == i, ]
  data <- data[!is.na(data$lag1_ret), ]
  data$YDAY <- as.numeric(strftime(data$date, format = "%j"))
  latitude <- metadata$Latitude[metadata$City == i]
  data$SAD <- daylength(latitude, data$YDAY)

  if (nrow(data) > 0) {

    # append the n and city vectors
    n[(length(n) + 1)] <- nrow(data)
    city[(length(city) + 1)] <- i

    # data transformations 
    data$pm25 <- data$pm25/10
    data$lag1_pm25 <- dplyr::lag(data$pm25, 1)
    data$lag2_pm25 <- dplyr::lag(data$pm25, 2)
    data$pm25_01 <- rollmean(data$pm25, 2, fill = NA, align = "right", na.pad = T)
    data$pm25_02 <- rollmean(data$pm25, 3, fill = NA, align = "right", na.pad = T)

    # fit the linear model 
    fit <- lm(formula, data = data, na.action = "na.exclude")
    return_models[[i]] <- fit

    # retrieve residuals for the GARCH models
    data$resid <- residuals(fit)
    temp_data <- data[!is.na(data$resid), ]

    # define the gjrGARCH(1,1) model specifications and run
    spec <- ugarchspec(variance.model = list(model = "gjrGARCH", garchOrder = c(1, 1)), mean.model=list(armaOrder=c(0,0), include.mean=TRUE), distribution.model = "norm")
    garch_fits[[i]] <- ugarchfit(spec, temp_data$resid)

    # retrieve predicted volatilities
    temp_data$vola <- garch_fits[[i]]@fit$sigma

    # run linear model on the garch volatilities
    formula2 <- formula(vola ~ pm25 + lag1_ret + lag2_ret + PRCP + WDSP + SLP + VISIB + temp_bins + dewp_bins + SAD + dow + woy)

    lm_fits[[i]] <- lm(formula2, data = temp_data, na.action = na.exclude)

  } else {
    next
  }
}

# summarize regression coefficient
return_estimates <- data.frame()
for (i in 1:length(return_models)){
  tryCatch({
    cf <- quiet(coeftest(return_models[[i]],vcov.=NeweyWest(return_models[[i]], prewhite = F, verbose = T))) 
    # apply NeweyWest standard errors
    p <- round(cf[,4], 4) 
    est <- round(cf[,1], 6)
    est <- sprintf("%.4f",est)
    temp <- ifelse(p < 0.10, paste(est, "*", sep = ""), paste(est))
    temp <- ifelse(p < 0.05, paste(temp, "*", sep = ""), paste(temp))
    temp <- ifelse(p < 0.01, paste(temp, "*", sep = ""), paste(temp))
    return_estimates <- bind_rows(return_estimates, temp)
  }, error=function(e){cat("ERROR :",i, "\n")}) 
  ## print out errors - used when testing with variables where certain cities would not converge
}

# filter out discreet variables and print out as formattable table
return_estimates <- cbind(city, return_estimates)
return_estimates <- return_estimates[,c(1, 3:9)]
formattable(return_estimates)
